\documentclass[11pt]{article}

\usepackage[a4paper, total={6in, 8in}]{geometry} % page layout
\usepackage{booktabs} % table
\usepackage{longtable} % longtable
\usepackage{kotex} % Korean
\usepackage[round,colon,authoryear]{natbib} % Reference

\begin{document}           

    \title{빅데이터 종합설계: Project Proposal}          
    \author{Sangsan Lee\textsuperscript{a},
        Jaeyoung Chun\textsuperscript{a},
        Junghyun Kim\textsuperscript{a},
        Keungoui Kim\textsuperscript{a}\\
    {\small \textsuperscript{a}School of Applied Aritifical Intelligence, Handong Global University}\\
    {\small 558 Handong-ro, Pohang-si, Gyeongbuk, South Korea}\\
        }

    \date{Spring Semester, 2023}      

 
    \maketitle                 
 
    \begin{abstract}
        Write down the brief summary of project proposal.
        300 words maximum. 초록은 영어로 쓰세요. 제안서는
        한국어로 작성해도 됩니다.
    \end{abstract}

    \tableofcontents
    \newpage
    
    \section{Introduction} 
    \subsection{Project background}
    Research background and motivation should be provided
    with a reliable reference \citep{Kim2018f, Kim2022}.    
    Remember that this section should address the 
    necessity of your project. 
    
    \subsection{Research question}
    Write down the research question in a bullet form.

    \begin{itemize}
        \item \emph{RQ 1: ~~}
        \item \emph{RQ 2: ~~}
        \item \emph{RQ ...}
    \end{itemize}

    \subsection{Project goal}
    Write down the project goal clearly and specifically.

    \section{Project Design}
    \subsection{Project plan}                       
    Write down the description of overall project 
    plan. Weekly Timeline should be provided.

    \subsection{Project participants}                       
    Introduce the project participants. A table should be 
    included.    

    \input{./table/participant_table.tex}   

    \section{Data}
    \subsection{Data resouce}
    Write down the description of data resource and 
    data collection process. 

    \subsection{Data pre-processing}
    Write down the data pre-processing strategy.

    \subsection{Data management}
    Write down how your team is planning to manage data
    source.

    \section{Method}                       
    \subsection{Methodologies}                       
    Write down the description of project Methodologies
    that you are going to use. You have to not only 
    explain what this methodology is, but also why it is 
    chosen. Remember that your methodological approach
    should be one of the Data Science methods. 

    \subsection{Analytic process}
    Describe the process of data analysis.

    \subsection{Validation strategy}
    Describe how you are going to validate your work.

    \section{Expected results}   
    Write down the expected results and how the outcome
    of your project can be used. Either theoretical or 
    practical implication should be mentioned.

    \bibliographystyle{apalike} % apalike 
    \bibliography{proposal_bib}

\end{document}
